\documentclass[11pt]{article}

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{natbib}
\usepackage{wrapfig}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{setspace}
\usepackage{comment}

\oddsidemargin 0cm
\evensidemargin 0cm

\usepackage[margin=1in]{geometry}

\parindent 0cm
\parskip 0.5cm

\usepackage{fancyhdr}
\pagestyle{plain}
%\fancyhf{}
%\fancyhead[L]{AOSS Reference Sheet}
%\fancyhead[CH]{test}
\fancyfoot[C]{Page \thepage}

\newcommand{\vb}{\mathbf}
\newcommand{\diff}[2]{\frac{d #1}{d #2}}
\newcommand{\diffsq}[2]{\frac{d^2 #1}{{d #2}^2}}
\newcommand{\pdiff}[2]{\frac{\partial #1}{\partial #2}}
\newcommand{\pdiffsq}[2]{\frac{\partial^2 #1}{{\partial #2}^2}}
\newcommand{\topic}{\textbf}
\newcommand{\arcsinh}{\mathrm{arcsinh}}
\newcommand{\arccosh}{\mathrm{arccosh}}
\newcommand{\arctanh}{\mathrm{arctanh}}

\begin{document}

\thispagestyle{empty}

\appendix

\setcounter{section}{5}

\section*{Biographical Sketch: Dr. Paul Ullrich}

\vspace{-0.5cm}
\begin{center}
\textbf{Ph:} (530) 400 9817, \textbf{Email:} \url{paullrich@ucdavis.edu}, \textbf{Web:} \url{http://climate.ucdavis.edu}
\end{center}

\vspace{-0.8cm}
\paragraph{\large (a) Professional Preparation}\ \\ \ \\
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lll}
University of Waterloo (Canada) & Applied Mathematics & B.Math 2005 \\
& \qquad and Computer Science & \\
University of Waterloo (Canada) & Applied Mathematics & M.Math 2007 \\
University of Michigan (Ann Arbor, USA) & Atmospheric Science & Ph.D. 2011 \\
& \qquad and Scientific Computing & \\
University of Michigan (Ann Arbor, USA) & Atmospheric Science & Postdoc 2011-2012 \\
& \qquad and Scientific Computing & \\
\end{tabular*}

\vspace{-0.5cm}
\paragraph{\large (b) Appointments and Professional Experience}\ \\ \ \\
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}ll}
09/12 - Present: & Assistant Professor, Regional and Global Climate Modeling, \\
& \qquad University of California Davis \\
05/11 - 08/12: & Postdoctoral Researcher / Adjunct Lecturer, \\
& \qquad University of Michigan, Ann Arbor, MI \\
09/04 - 12/04: & Mathematics Developer, Maplesoft Inc., Waterloo, Canada \\
01/04 - 04/04: & Senior Software Engineer, RapidLabs Microsystems, Waterloo, Canada \\
01/01 - 08/02: & Software Engineer, Sonic Foundry Canada, Waterloo, Canada
\end{tabular*}

\vspace{-0.3cm}
\paragraph{\large (c) Publications}\ \\
\vspace{-0.8cm}
\begin{itemize}
\item \textbf{Ullrich, P.A.} and Taylor, M.A. (2015) ``Arbitrary-Order Conservative and Consistent Remapping and a Theory of Linear Maps, Part 1.''  Submitted to Mon. Weather Rev.

\item \textbf{Ullrich, P.A.} (2014) ``A global finite-element shallow-water model supporting continuous and discontinuous elements.''  Geosci. Model Dev. Discuss., Vol. 7, 5141--5182, doi: 10.5194/gmdd-7-5141-2014.

\item \textbf{Ullrich, P.A.} (2014) ``Understanding the treatment of waves in atmospheric models, Part I: The shortest resolved waves of the 1D linearized shallow water equations.'' Quart. J. Roy. Meteor. Soc., Vol. 140, 1426--1440, doi: 10.1002/qj.2226. 

\item \textbf{Ullrich, P.A.}, T. Melvin, C. Jablonowski and A. Staniforth (2014) {``A proposed baroclinic wave test case for deep- and shallow-atmosphere dynamical cores.''}  Quart. J. Royal Meteor. Soc., Vol. 140, 1590--1602, doi: 10.1002/qj.2241. 

\item \textbf{Ullrich, P.A.}, P.H. Lauritzen and C. Jablonowski (2013) {``Some considerations for high-order `incremental remap'-based transport schemes: edges, reconstructions and area integration.''}  Int. J. Numer. Meth. Fluids., Vol. 71, 1131--1151, doi: 10.1002/fld.3703.
\end{itemize}

\vspace{-0.5cm}
\paragraph{\large (d) Synergistic Activities}\ \\
\vspace{-0.8cm}
\begin{itemize}
\item Associate Editor of the AMS journal Monthly Weather Review (MWR).  Lead developer of the Tempest finite-element Earth-system modeling framework.  Co-developer of the Chombo/MCore finite-volume dynamical core (at Lawrence Berkeley National Lab).
\end{itemize}

\end{document}
