% Upper-case    A B C D E F G H I J K L M N O P Q R S T U V W X Y Z
% Lower-case    a b c d e f g h i j k l m n o p q r s t u v w x y z
% Digits        0 1 2 3 4 5 6 7 8 9
% Exclamation   !           Double quote "          Hash (number) #
% Dollar        $           Percent      %          Ampersand     &
% Acute accent  '           Left paren   (          Right paren   )
% Asterisk      *           Plus         +          Comma         ,
% Minus         -           Point        .          Solidus       /
% Colon         :           Semicolon    ;          Less than     <
% Equals        =           Greater than >          Question mark ?
% At            @           Left bracket [          Backslash     \
% Right bracket ]           Circumflex   ^          Underscore    _
% Grave accent  `           Left brace   {          Vertical bar  |
% Right brace   }           Tilde        ~

%
% NSF Biographical Sketch: Dr. Theodore P. Pavlic
%
% Copyright (c) 2013 by Theodore P. Pavlic
% All rights reserved.
%

\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{times}
\renewcommand\thesection{(\alph{section})}
\renewcommand\thesubsection{(\alph{subsection})}

\usepackage{calc}

\usepackage{lastpage}
%\newcommand{\pageoflastpage}{Page {\thepage} of \pageref*{LastPage}}
%\newcommand{\pageoflastpage}{{\thepage} of \pageref*{LastPage}}
\newcommand{\pageoflastpage}{}

% Redefine the plain pagestyle for the title page
\makeatletter
\let\oldps@plain\ps@plain
\renewcommand{\ps@plain}{\oldps@plain%
\renewcommand{\@evenfoot}{\hfil\pageoflastpage\hfil}%
\renewcommand{\@oddfoot}{\@evenfoot}}
\makeatother

% Use fancy for non-title pages
\usepackage{fancyhdr}
\fancyhead{}
\fancyfoot{}
\cfoot{\pageoflastpage}
\pagestyle{fancy}

\usepackage{xspace}

\usepackage[shortlabels]{enumitem}
\usepackage{graphicx}
\usepackage{varioref}
\usepackage[%
        colorlinks=true,urlcolor=,
        pdfpagelabels=true,hypertexnames=true,
        plainpages=false,naturalnames=true,
        ]{hyperref}
%
\usepackage{url}
\newcommand\doilink[1]{\href{http://dx.doi.org/#1}{#1}}
\newcommand\doi[1]{doi:\doilink{#1}}

\makeatletter
\newlength{\bibhang}
\setlength{\bibhang}{1em}
\newlength{\bibsep}
 {\@listi \global\bibsep\itemsep \global\advance\bibsep by\parsep}
\newlist{bibsection}{itemize}{3}
\setlist[bibsection]{label=,leftmargin={\bibhang+\widthof{[9]}},%
        itemindent=-\bibhang,
        itemsep=\bibsep,parsep=\z@,partopsep=0pt,
        topsep=0pt}
\newlist{bibenum}{enumerate}{3}
\setlist[bibenum]{label=\textbf{\arabic*.},leftmargin={\bibhang+\widthof{[999]}},%
        itemindent=-\bibhang,
        itemsep=\bibsep,parsep=\z@,partopsep=0pt,
        topsep=0pt}
\let\oldendbibenum\endbibenum
\def\endbibenum{\oldendbibenum\vspace{-.6\baselineskip}}
\let\oldendbibsection\endbibsection
\def\endbibsection{\oldendbibsection\vspace{-.6\baselineskip}}
\makeatother

\title{%
        \vspace{-2\baselineskip}
            \normalsize
            Biographical Sketch\\
            {\normalsize\textbf{Dr. Colin M. Zarzycki}}\\
            \vspace{0.5\baselineskip}
            \hrule
            \vspace{0.5\baselineskip}
            Advanced Study Program (ASP), Climate and Global Dynamics Division (CGD)\\
            National Center for Atmospheric Research (NCAR),
            E-mail: \href{mailto:zarzycki@ucar.edu}{zarzycki@ucar.edu},
            Phone: (303) 497-1381
        \vspace{-1.5ex}
        }
\date{}
\author{}

\newcommand{\ie}{i.e.\xspace}
\newcommand{\eg}{e.g.\xspace}

\begin{document}

\maketitle
\vspace{-4\baselineskip}

\subsection*{Education}

    Cornell University, Ithaca, NY;
        Earth and Atmospheric Science;
        B.S., 2008
        \\
    University of Illinois, Urbana, IL;
        Civil and Environmental Engineering;
        M.S., 2010
        \\
    University of Michigan, Ann Arbor, MI;
        Atmospheric, Oceanic, and Space Sciences;
        Ph.D., 2014

\subsection*{Appointments}

\begin{itemize}[label={\quad 9999--9999:},leftmargin=*,itemsep=0pt]

    \item[2014--present:]
        \textbf{Advanced Study Program (ASP) Postdoctoral Fellow},
        National Center for Atmospheric Research,
        Boulder, CO

    \item[2014:]
        \textbf{Postdoctoral Researcher},
        University of Michigan,
        Ann Arbor, MI

\end{itemize}

\subsection*{Recent publications}

\begin{bibenum}[itemsep=0pt]
\item {\bf Colin M. Zarzycki}, Christiane Jablonowski, Diana R. Thatcher, Mark A. Taylor (2015), ``Effects of localized grid refinement on general circulation and climatology in the Community Atmosphere Model.'' {\em J. Clim}, in press.
\item Kevin J.E. Walsh, [...], {\bf Colin M. Zarzycki}, {\it et al.}, (2014), ``Hurricanes and climate: the U.S. CLIVAR working group on hurricanes.'' {\em B. Am. Meteorol. Soc.}, in press. \href{http://dx.doi.org/10.1175/BAMS-D-13-00242.1}{doi:10.1175/BAMS-D-13-00242.1}.
\item {\bf Colin M. Zarzycki}, Christiane Jablonowski (2014), ``A multidecadal simulation of Atlantic tropical cyclones using a variable-resolution global atmospheric general circulation model.'' {\em J. Adv. Model. Earth Syst.}, {\bf6}(3), 805--828, \href{http://dx.doi.org/10.1002/2014MS000352}{doi:10.1002/2014MS000352}.
\item {\bf Colin M. Zarzycki}, Michael N. Levy, Christiane Jablonowski, Mark A. Taylor, James Overfelt, Paul A. Ullrich (2014), ``Aquaplanet experiments using CAM's variable-resolution dynamical core.'' {\em J. Clim.}, {\bf27}(14), 5481--5503, \href{http://dx.doi.org/10.1175/JCLI-D-14-00004.1}{doi:10.1175/JCLI-D-14-00004.1}.
\item {\bf Colin M. Zarzycki}, Christiane Jablonowski, Mark A. Taylor (2014), ``Using variable-resolution meshes to model tropical cyclones in the Community Atmosphere Model.'' {\em Mon. Wea. Rev.}, {\bf142}(3), 1221--1239,  \href{http://dx.doi.org/10.1175/MWR-D-13-00179.1}{doi:10.1175/MWR-D-13-00179.1}.
\item Tami C. Bond, {\bf Colin Zarzycki}, Mark G. Flanner, Dorothy M. Koch (2011), ``Quantifying immediate radiative forcing by black carbon and organic matter with the Specific Forcing Pulse'', {\em Atmos. Chem. Phys.}, {\bf11}, 1505--1525, \href{http://dx.doi.org/10.5194/acp-11-1505-2011}{doi:10.5194/acp-11-1505-2011}.
\item {\bf Colin M. Zarzycki}, Tami C. Bond (2010), ``How much can the vertical distribution of black carbon affect its global direct radiative forcing?'', {\em Geophys. Res. Lett.}, {\bf37}, L20807, \href{http://dx.doi.org/10.1029/2010GL044555}{doi:10.1029/2010GL044555}. 
\end{bibenum}

\subsection*{Synergistic Activities}

Co-convener and chair of sessions at both American and European Geophysical Union Annual Meetings; Reviewer for Journal of Climate, Journal of Geophysical Research-Atmospheres, Journal of Advances in Modeling the Earth System, Science of the Total Environment, Michigan Journal of Sustainability; Member of the NCAR Thompson Lecture Series Committee.

%\subsection*{Collaborators \& Co-authors}

\end{document}
