\documentclass[11pt]{article}

\usepackage{graphicx}
\usepackage{natbib}
\usepackage{float} % Needed to force figure dump in specific location. Use [H] option.
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\begin{document}

\title{Scope of Work}
\date{}

%\maketitle

\begin{center}
\Large Scope of Work \\ [0.5cm]

\large \textbf{PI:} Dr. Paul Ullrich \\
\large \textbf{Subcontract Co-I:} Dr. Colin Zarzycki \\[0.25cm]

\large \textbf{Project Title:} TempestExtremes: Indicators of change in the characteristics of extreme weather \\ [0.5cm]%\large Project start / end: 09/01/2012 ? 08/31/2017 \\ [0.5cm]
\hrule

\end{center}

Dr. Colin Zarzycki will consult with Dr. Paul Ullrich regarding the implementation of cyclone detection within the TempestExtremes framework. In particular, he will aid in configuring the software to produce results consistent with previously published techniques. He will also develop methods for detecting the sensitivity of parameters in the tracking algorithms. Based on this and his previous results, he will offer suggestions for configurations which produce skillful detection of both tropical and extratropical cyclones in weather and climate data.

Travel reimbursement is budgeted at approximately \$2,800 in order to travel to UCDavis for consulting and collaborative efforts as well as one domestic conference or workshop per year to present findings from the project and discuss potential avenues for improvement or future work.
Indirect costs are calculated at XX\%.

\end{document}
